Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-26 robdml.tex
svg
tex

\textbf{Destination Hardness} $H_\mathsf{D}$.
%
$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ is a very flexible method as various
\emph{destination} hardness $H_\mathsf{D}$ can be used, \eg, a constant, the
hardness of another benign triplet, or even a pseudo-hardness function.
%
The case of maximizing the triplet loss is equivalent to
$\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
upperbound of triplet loss.

@@

@@

We propose an additional loss function term to enforce such \emph{intra-class}
structure, as shown in \oo{Fig.~[].}
%
Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
are separated from the positve sample $\vp$ by reusing the triplet loss,
\ie,
%
\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0),
\end{equation}
%
where $\lambda$ is a constant weight for this loss term,
and the margin is set as zero to avoid negative effect.
%
The $L_\text{ICS}$ term can be added to the loss function for
adversarial training.

>>>>

\textbf{Destination Hardness}.
%
$\text{HM}[H_\mathsf{S},H_\mathsf{D}]$ is flexible as various
types of $H_\mathsf{D}$ can be specified, \eg, a constant, the
hardness of another benign triplet, or even a pseudo-hardness function.
%
The case of maximizing the triplet loss is equivalent to
$\text{HM}[H_\mathsf{S},2+\gamma]$, where $2+\gamma$ is the 
upperbound of loss, while $\text{HM}[H_\mathsf{S},H_\mathsf{S}]$
is regular DML training.

@@

\begin{figure}[t]
	\includegraphics[width=0.6\columnwidth]{icsapn.pdf}
	\caption{Intra-Class Structure.}
	\label{fig:ics}
\end{figure}

@@

We propose an additional loss function term to enforce such \emph{intra-class}
structure, as shown in \cref{fig:ics}.
%
Specifically, the anchor $\va$ and its adversarial counterpart $\tilde{\va}$
are separated from the positve sample $\vp$ by reusing the triplet loss,
\ie,
%
\begin{equation}
	L_\text{ICS} = \lambda \cdot L_\text{T}(
	\va, \tilde{\va}, \vp; 0),
\end{equation}
%
where $\lambda$ is a constant weight for this loss term,
and the margin is set as zero to avoid negative effect.
%
The $L_\text{ICS}$ term can be added to the loss function for
adversarial training.
